---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



# Automated Retrieval of ACLED Conflict Event Data

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/chris-dworschak/acled.api.svg?branch=master)](https://travis-ci.com/chris-dworschak/acled.api)
<!-- badges: end -->

This small package makes it easy to automatically retrieve a user-defined sample or all available data of ACLED: the package provides functionality to access and manage the application programming interface (API) of the Armed Conflict Location & Event Data Project (ACLED) at https://www.acleddata.com. 

When using this package, you acknowledge that you have read ACLED's terms and conditions of use, and that you agree with their attribution requirements.




## Installation

You can install the released version of acled.api from [CRAN](https://CRAN.R-project.org) with: 

``` r
install.packages("acled.api")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chris-dworschak/acled.api") # downloads and installs the package
```


## Example

Using acled.api is straight forward. To download data on, for example, all ACLED conflict events in Europe and Central America that happened between June 2019 and July 2020, you can supply:


```{r example}
library(acled.api) # loads the package

my.data.frame <- acled.api( # stores an ACLED sample in object my.data.frame
  regions = c(12,14), 
  start.date = "2019-06-01", 
  end.date = "2020-07-31")

head(my.data.frame) # returns the first five observations of the ACLED sample
```
